---
title: "HW1 submission TPD2121"
output: html_document
date: "2024-09-20"
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Problem 1

```{r load, include=FALSE}
data("penguins", package = "palmerpenguins")
```

### Description

The penguins dataset contains `r nrow(penguins)` rows/observations and `r ncol(penguins)` columns/variables. The 8 variables observed in this dataset are penguin species, island where they are observed, bill length (in mm), bill depth (in mm), flipper length (in mm), body mass (in gr), sex, and year of observation. Species, island, and sex are all characters (or factors) data type, while the rest are numeric data. 

The mean for bill length are `r mean(pull(penguins, flipper_length_mm), na.rm=TRUE)` mm. 

### Scatterplot

```{r scatterplot, echo = FALSE, message=FALSE, warning=FALSE}
ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color=species)) + geom_point()

ggsave("plot_penguins.pdf",width=5,height=5)
```

## Problem 2

Data frame:

```{r df}
la_df = tibble(
  df_samp = rnorm(10),
  df_logical = df_samp > 0, 
  df_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"), 
  df_factor = c("small", "small", "small", "medium", "medium", "big", "big", "big", "big", "big")
)
```

The mean for the first variable is `r mean(pull(la_df, df_samp))`
<br>
The mean for second variable is `r mean(pull(la_df, df_logical))`
<br>
The mean for third variable is `r mean(pull(la_df, df_char))`
<br>
The mean for fourth variable is `r mean(pull(la_df, df_factor))`


